\cvsection{Experiences}
\begin{cventries}
  \cventry
    {Developer Intern, Point of Sale Team}
    {Shopify Inc}
    {Ottawa, ON}
    {Sep 2017 - Dec 2017}
    {
      \begin{cvitems}
        \item {Worked on improving the checkout experience by collaborating on major code refactor and various design tweaks.}
        \item {Identified and fixed 3 long-lasting mysterious failures just in time during Black Friday when some merchants could not sell at all.}
        \item {Made 100+ people laugh during my Hack Days presentation.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer Intern, iOS Team}
    {The Meet Group (formerly if(we))}
    {San Francisco, CA}
    {May 2017 - Aug 2017}
    {
      \begin{cvitems}
        \item {Built on top of Buildasaur, an open source continuous integration tool, and kept compiler warnings in the repository at 0 forever.}
        \item {Designed and developed various on-device debugging tools, including an A/B Testing controller that can switch variant assignments on demand. Dramatically increased productivity of developers and QAs.}
      \end{cvitems}
    }
  \cventry
    {Associate Engineer, Engagement Team}
    {Wattpad}
    {Toronto, ON}
    {Sep 2016 - Dec 2016}
    {
      \begin{cvitems}
        \item {Conducted various experiments with A/B Testing, increased average story reading time by 5\%.}
        \item {Promoted adoption of Swift and Auto Layout; cleared engineering roadblocks.}
      \end{cvitems} 
    }
  \cventry
    {Software Engineer, iOS Team}
    {WeMesh Inc}
    {Kitchener, ON}
    {Jan 2016 - Apr 2016}
    {
      \begin{cvitems}
        \item {Reduced memory usage from 150MB to 70MB, and saved \textasciitilde60\% cpu usage by profiling with Instruments.}
      \end{cvitems}
    }
  \cventry
    {Software Engineering in JavaScript, Campaigns Team}
    {Hootsuite Media Inc}
    {Vancouver, BC}
    {May 2015 - Aug 2015}
    {
      \begin{cvitems}
        \item {Developed pages for creating and managing contests and sweepstakes, including an image editing tool as a node module. Worked with Webpack, Gulp, jQuery and Laravel PHP. }
      \end{cvitems}
    }
\end{cventries}
